---
title: "Statistical Inference Course Project part 2"
author: "Louis"
date: "9/20/2020"
output: pdf_document
---
# Coursera Statistical Inference Course Project
```{r}
library(ggplot2)
library(dplyr)
library(knitr)
```

# Part 2 : Sorting out the Tooth Growth Data
```{r}
# Load the Data
data <- read.csv("ToothGrowth.csv")
# Renaming the columns for more easier understanding
data <- rename( data,Number = X, Length = len, Supplement = supp, Dose = dose)
# Due to there being an select type of Doses, change it to a factor
data$Dose <- as.factor(data$Dose)
```

# Plotting the data to make more sense of it
```{r}
theplot1 <- ggplot(data = data, aes(x = Dose, y = Length))
theplot1 + geom_boxplot(aes(fill = Dose)) + 
        labs(title = "Different doses based on tooth length")


theplot2 <- ggplot(data = data, aes(x = Supplement, y = Length))
theplot2 + geom_boxplot(aes(fill = Supplement)) + 
        labs(title = "Different tooth length based on supplement")

theplot3 <- ggplot(data = data, aes(Dose, Length))
theplot3 <- theplot3 + geom_boxplot(aes(fill = Supplement)) + 
        facet_grid(~ Supplement)
theplot3 + labs(title = "Different Doses based type of Supplement")

```

## P-values of the data: 
## If p-value is bigger than level of significance(0.05) then there is a correlation
## between the data.
```{r}
# Comparing Length and Supplement
t.test(Length~Supplement, data=data)
# There is no correlation with different supplements and tooth length 

# Comparing length with 0.5mg and 2mg doses
t.test(data$Length[data$Dose == 0.5],data$Length[data$Dose == 2], data=data)
# There is a correlation between tooth length and dose(0.5mg and 2mg)

# Comparing length with 0.5mg and 1mg doses
t.test(data$Length[data$Dose == 0.5],data$Length[data$Dose == 1], data=data)
# There is a correlation between tooth length and dose(0.5mg and 1mg)

# Comparing length with 1mg and 2mg doses
t.test(data$Length[data$Dose == 1],data$Length[data$Dose == 2], data=data)
# There is a correlation between tooth length and dose(1mg and 2mg)
```

# Conclusion: 
## There is a direct correlation between the dose and the tooth length.
## We can assume that with an larger tooth length, the dose will increase as well.
## There is no correlation with the type of supplement and tooth length.

 